### 2016-07-01 store-consistency.tex
Fixed typo.

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality owing to the subtle differences in the semantics of isolation
levels among databases. For instance, Postgres's \iso{Repeatable Read}
isolation is stronger than ANSI SQL's or MySQL's in non-trivial ways.
Furthermore, the need for high availability on geo-replicated stores
has led to the development of of new isolation levels which are yet to
be standardized. For example, \emph{Parallel Snapshot
Isolation}~\cite{psi} was proposed in 2011, and \emph{Non-Monotonic
Snapshot Isolation}~\cite{nmsi} in 2013, both targeted for replicated
stores. As more commercial weakly consistent stores adopt variants of
transactions (like the \emph{lightweight transactions} of Cassandra),
it is reasonable to expect novel forms of isolation to be proposed.
While it is possible to carefully engineer a reasoning framework for
each combination of consistency and isolation, it leads to multiple
proof systems with no obvious to compare proofs.  Having a
parameterized semantics and proof framework built on this semantics
allows us to support these variants as distinct, yet comparable
instantiations, thus avoiding the need for semantics re-engineering
every time an application is retargeted to a new platform

>>>>

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting is one of
the characteristic our reasoning approach. While intuition suggests
that some instantiations, such as {\sc sc} with ANSI SQL isolation,
are general enough to cover many practical cases, it not the case in
reality owing to the subtle differences in the semantics of isolation
levels among databases. For instance, Postgres's \iso{Repeatable Read}
isolation is stronger than ANSI SQL's or MySQL's in non-trivial ways.
Furthermore, the need for high availability on geo-replicated stores
has led to the development of of new isolation levels which are yet to
be standardized. For example, \emph{Parallel Snapshot
Isolation}~\cite{psi} was proposed in 2011, and \emph{Non-Monotonic
Snapshot Isolation}~\cite{nmsi} in 2013, both targeted for replicated
stores. As more commercial weakly consistent stores adopt variants of
transactions (like the \emph{lightweight transactions} of Cassandra),
it is reasonable to expect novel forms of isolation to be proposed.
While it is possible to carefully engineer a reasoning framework for
each combination of consistency and isolation, it leads to multiple
proof systems with no obvious way to compare proofs.  Having a
parameterized semantics and proof framework built on this semantics
allows us to support these variants as distinct, yet comparable
instantiations, thus avoiding the need for semantics re-engineering
every time an application is retargeted to a new platform
